Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities

### 2023-12-07 paper/manuscript.Rmd
New introduction: highlighting research gap

Global environmental change including climate, land use and invasive species
constitutes a suite of major threats to biodiversity and ecosystem functioning
[@pachauri_climate_2015; @simmons_refocusing_2021]. A central feature of these
threats is that they are predicted to dramatically increase variability in the
environment that species face [@pachauri_climate_2015] with potential impacts on
the stability of communities and associated impacts on biodiversity and
functioning in these communities. Assessing the impacts of this variability on
communities is challenging for several reasons.

First, there are numerous definitions of community stability depending of the
stressors considered. For example, resistance and resilience are typically used
when a pulse perturbation is considered [@kefi_advancing_2019]. While in natural
settings where press and pulse perturbations are simultaneously present,
community variability measured as the coefficient of variation is typically used
[@thibaut_understanding_2013]. Defined at the community scale, community
variability can be partitioned into population stability and asynchrony
[@thibaut_understanding_2013]. Synchronous population fluctuations will amplify
the negative effects of environmental fluctuations on temporal community
stability while compensatory dynamics and portfolio effects (i.e. asynchrony)
will stabilise temporal fluctuations of community biomass [@shoemaker_long_2022;
@zhao_biodiversity_2022]. Environmental forcing (such as food availability and
warming) and land-use intensity was reported to synchronise population
fluctuations [@benton_population_2001; @bluthgen_land_2016; @song_reduced_2015;
@liu_aridity_2023] while habitat degradation tends to decrease population
stability [@olivier_urbanization_2020]. Understanding the effects of global
change on community temporal stability therefore require to account for their
simultaneous effects on community and population scales [@kefi_advancing_2019;
@simmons_refocusing_2021].

Second, the relation between community stability and biodiversity in variable
environment is contingent on species richness per se, on the effects of species
richness on population stability and asynchrony, and ultimately
on the diversity of species responses to environmental fluctuations [response
diversity, @ives_stability_2000; @elmqvist_response_2003]. Increasing
species richness has been reported to decrease population stability in
experimental grasslands [@tilman_biodiversity_2006; @roscher_identifying_2011],
while increasing population stability in natural settings
[@houlahan_negative_2018] [add mechanisms?]. In turn, higher species richness
often results in higher asynchrony, through portfolio effects (i.e. statistical
averaging effects due to independent species fluctuations) and compensatory
dynamics (due to species interactions and response
diversity of species due to the environment) [@loreau_species_2008;
@thibaut_understanding_2013]. Systematic increase in asynchrony with species
richness is the mechanism that drives reported positive relationships between
community stability and species richness [ref]. Anthropogenic pressures, such as
eutrophication, has been reported to weakens the relationship between species
richness and asynchrony in grasslands [@hautier_eutrophication_2014] but such
empirical evidence remains scarce. However, stressors such as biotic
homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
@saladin_rapid_2020] and environmental forcing that decrease species response
diversity should dampens the relationships between asynchrony and species
richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
in portfolio effects and compensatory effects. [Talk about the effects of
evenness in temporal variability and evenness in abundance? e.g.,
@zhao_biodiversity_2022; @thibaut_understanding_2013]. Because stressors can
affect both community stability per se and how community stability scales with
species richness, improving our understanding require to study both
[@ives_stability_2007; @hautier_anthropogenic_2015].

Third, the structure of species trophic interactions, that determines the
distribution of biomass fluxes through communities, can also control stability.
including levels of generalism, the distribution of interaction strengths and
the prevalence of omnivory, can also influence stability. The degree of
generalism of predator was shown to modulate stability-richness relationships
[@thebault_trophic_2005], and generalist predators can synchronise the dynamics
of their preys[@raimondo_interspecific_2004]. The strength and distribution of
interaction strength was also shown to be strong driver of community stability,
such as stronger interaction strengths can be destabilizing [@may_will_1972;
@mccann_weak_1998]. Omnivory was also shown to drive higher population stability
[@mccann_reevaluating_1997]. The effects of food-web structure on ecosystem
stability has been mostly assessed with small modules [but see
@eschenbrenner_diversity_nodate], and we know very little how food-web structure
affects the relationships between species richness and temporal stability in
complex food-webs. So understanding the effects of stressors on community
stability and on community stability-richness relationships necessitate to
account for food-web structure.

Here we deliver inference from modelling of complex biodiverse communities on
how food-web structure (connectance, average interaction strength, average
trophic level), response diversity, and environmental stochasticity combine to
shape temporal stability of community biomass, as well as its partition into
asynchrony and population stability. We then assess how food-web complexity and
response diversity shape stability-richness relationships.

@@

@@

We added a stochastic natural mortality rate to the species dynamics,
representing a fluctuating environment. Based on the literature and previous
models [@vasseur_environmental_2007], we assumed that
natural mortality rates scales inversely with the species body mass ($d_i =
d_0M_i^{-1/4}$, ), as all other physiological parameters. We used a basal
natural mortality rate of $d_0 = .4$, as done in previous
studies[@vasseur_environmental_2007].

@@

To vary interaction strength and mortality rates in the community,
we varied the Predator-Prey Bodysize Ratio (PPBR) from 1 to 100. We further
varied the functional response of consumer from type II to type III (resp. $h=2$
and $h=3$, eq XX) as it was shown to have a tremendous role on stability
[@brose_allometric_2006]. We set $K = XX$ to ensure that consumers were not
limited by the biomass input from primary producers.

@@

We numerically solved the simulations with a $dt$ = .1 during 5000 timesteps
and collected the last 500 timesteps. We set extinction threshold to $10^{-5}$
and if an extinction happened in the last 500 timesteps, we continued to run the
simulation for another 500 timesteps until there was no extinction events.

@@

Regarding asynchrony, we tested the effects of species richness, connectance,
average trophic level and interaction strength on statistical averaging effects.
We expected that those same food-web structural properties affected
compensatory dynamics due to interactions ($CPE_{int}$). Finally, we tested the
effects of species richness and species cross-correlation in mortality rates on
the compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We
completed the structural equation model with the mathematical relationship
linking compensatory dynamics and statistical averaging effects to asynchrony,
and from asynchrony and population stability to community stability.

@@

In a second analysis, we aimed to test how stability-species richness
relationships were modulated by food-web structure and the two stressors:
environmental stochasticity and response diversity. We modelled temporal
stability of biomass according to food-web structure: species richness, weighted
average trophic level, connectance, hill exponent, predator-prey size ratio, and
average interaction strength, as well as environmental stochasticity and species
cross-correlation. We further included the two way interactions between species
richness and food-web structure, plus between species richness and stressors.
Finally we added the three way interaction between species richness, food-web
structure and stressors. The VIF were inferior to 5, indicating low
multicollinearity. We then used the coefficients of the model to predict the shape
of the relationship between community stability and species richness according
to a gradient of response diversity and of food-web structure.

@@

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  cross-correlation among species mortality rates (Env. correlation). We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. A more complete SEM containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

@@

rcr <- get_eff(y = "cpe", x = "richness")
rci <- get_eff(y = "cpe", x = "avg_int_strength")
rco <- get_eff(y = "cpe", x = "rho")

@@

rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
rvo <- get_eff(y = "cpe_env", x = "rho", tab = sem_eff_tab)
```
```{r, eval = FALSE}
sem_simplified_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```

@@

We further found that food-web structure had a strong impact on statistical
averaging effects, which raises from independent species fluctuations weighted
the evenness of their variance. As expected the mathematical relationship (eq.
XX), species richness was a main positive driver of statistical averaging effect
($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)), thereby increasing asynchrony.
Average trophic level and average interaction strength had strong negative
effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
`r rsi`), thereby downplaying the portfolio effect raised from species
richness. In turn, we found that average interaction strength had a small
positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
\@ref(fig:sem)). Cross-correlation among species mortality rates (i.e. lower
response diversity) had a strong negative effect on compensatory dynamics
($r_\delta$= `r rco`), meaning that the loss of response diversity result in a
strong decrease in compensatory dynamics.

@@

```{r}
rtsrho <- get_eff(y = "stab_com", x = "rho", effect_type = "total")
rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")

@@

Deriving the sum of direct and indirect effects from the structural equation
model, we show that both environmental stochasticity and cross-correlation among
species had by far the most negative effect on community stability (resp.
$r_\delta$= `r rtsenv` and `r rtsrho`, Fig. \@ref(fig:semtot)). Species richness
had a low overall positive total effect on community stability (`r rtsr`)
because its strong total positive effect on asynchrony (`r rtar`) was downplayed
by its total negative effect on population stability (`r rtpr`) and that the
weight of population stability on community stability is twice higher than the
one of asynchrony. Average trophic level, type III functional response and
predator prey bodysize ratio had positive effects on community stability in
total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:semtot)), driven by
their positive effects on population stability that were weakly counterbalanced
by their negative effects on asynchrony. In turn, connectance and average
interaction strength had low total negative effects on community stability (resp.
`r rtsc` and `r rtsi`, Fig. \@ref(fig:semtot)). While connectance had negative
effects both on population stability and asynchrony, average interaction
strength had a low total positive effect on population stability counterbalanced
by a stronger negative effect on asynchrony.

@@

```{r}
tar_load(default_variable_values_pred)
pv <- default_variable_values_pred
pv_cap <- paste0(
  "connectance = ", pv["ct_alive"],
  ", average interaction strength = ", pv["avg_int_strength"],
  ", average trophic level = ", pv["w_avg_tlvl"],
  ", hill exponent = ", pv["h"],
  ", Predator-Prey Mass Ration = ", pv["Z"],
  ", environmental correlation = ", pv["rho"],
  ", and environmental stochasticity = ", pv["env_stoch"]

@@

Using a more complex linear model (i.e. including interactions), we investigated more
in detail the relationship between community stability and species richness and
how this relation is affected by environmental stochasticity and cross
correlation among species mortality rates. We found that environmental
stochasticity decrease overall community stability but has only little effect on
the shape of the community stability-species richness relationship (put some
numbers, Fig. \@ref(fig:pred)a and b). In contrasts, cross correlation among
species mortality rates both decreases overall community stability and nullifies
the community stability-species richness relationship. Surprisingly, we found that
despite average interaction strength has a small overall effect on
community stability, high average interaction strength change the shape of the
community stability-species richness relationship from positive to negative when
response diversity is low (put some numbers, Fig. \@ref(fig:pred)b).

>>>>

Global environmental change constitutes a suite of major threats to biodiversity
and ecosystem functioning [@lee_ipcc_2023; @simmons_refocusing_2021]. A central
feature of these threats is that they are predicted to dramatically increase
variability in the environment that species face [@lee_ipcc_2023] with potential
impacts on the stability of communities and associated impacts on biodiversity
and functioning in these communities. Assessing the impacts of this variability
on communities is challenging for several reasons.

First, the stability of communities is often evaluated using temporal
variability the metric of interest (e.g. abundance or biomass), because most
natural communities face persistent perturbations so that other stability
metrics such as resilience and resistance are not always applicable
[@arnoldi_resilience_2016]. Understanding temporal community variability,
measured as the inverse of the coefficient of variation
[@tilman_biodiversity_2006; @roscher_identifying_2011;
@thibaut_understanding_2013; @zhao_biodiversity_2022], requires to scale down
the focus to populations. Community stability can be mathematically partitionned
into average population stability and asynchrony [@loreau_species_2008;
@thibaut_understanding_2013; @zhao_biodiversity_2022], asynchrony measuring how
much each species fluctuations are compensating each other at the community
level. Population stability and asynchrony depend both on the number of species
and their dominance [@loreau_species_2008; @thibaut_understanding_2013; @zhao_biodiversity_2022],
the interactions among them [@thebault_trophic_2005;
@thebault_relationship_2006; @loreau_species_2008; @danet_species_2021;
@eschenbrenner_diversity_nodate] and on the way that species respond to
environmental perturbations [response diversity, @ives_stability_2000;
@elmqvist_response_2003; @ross_how_2023]. Therefore, accounting for the effects
on community structure on population stability and asynchrony is crucial to
improve our understanding of community stability in face of environmental
change.

Average population stability is decreased by external forcing, such as the
intensity and the frequency of perturbations [@ref]. Species richness can
decrease [@tilman_biodiversity_2006; @loreau_species_2008], increase
[@houlahan_negative_2018], or have little effects on population stability. This
effect of species richness on population stability depends on the evenness of
the community such as dominant species contribute more the average of the
community than surbordinate species. At the core of ecological theory,
population stability depends on internal forcing, here species interactions. The
topogical structure and the distribution of interaction strength have tremendous
effects on population stability, such as strong interaction strength are
generally destabilising [@mccann_weak_1998; @mccann_reevaluating_1997;
@thebault_trophic_2005]. In particular for food-webs, top-down and bottom-up
controls can increase population stability.

Asynchrony in turn can be partitionned into portefolio effects and compensatory
dynamics and is mostly determine by internal factors. Portefolio effects stems
from the statistical averaging of independent population fluctuations
[@doak_statistical_1998; @zhao_biodiversity_2022], thereby increasing
asynchrony. Compensatory dynamics in turn captures population fluctuations that
are more synchronous or asynchronous than expected for independant fluctuations,
and can stem from species interactions and species responses to perturbations
[@zhao_biodiversity_2022]. Response diversity captures how among species’
differences in their response to the environmental variation, can underpin
asynchronous dynamics if their responses are different but synchronous if their
responses are similar. Theory and empirical data emerging around response
diversity suggests it is  “core ecological mechanism underpinning many of the
statistical explanations of the diversity–stability relationships”
[@ives_stability_2000; @elmqvist_response_2003; @ross_how_2023]. In turn,
the distribution and strength of species interactions can also modulate
asynchrony through compensatory dynamics such as a strong asymetry of consumer
preference can generate asynchrony in resource fluctuations [@mccann_weak_1998;
@vasseur_environmental_2007], and a generalist consumer can in turn generate
synchrony among its prey [@raimondo_interspecific_2004]. Competition can also
have synchronising effects in strong species growth rates regime
[@loreau_species_2008]. Finally, portefolio and compensatory effects can also be
affected by the population evenness such as fluctuations of a dominant
species will be hardly compensated by a subordinate species. Improving our
understanding of community stability facing perturbations therefore requires to
articulate the effect response diversity, species interactions, species
richness and evenness on the different components of stability.

The stability of ecological communities facing perturbations stems from two
parallel bodies of work: species interactions and response diversity. These two
bodies of work share the common thread of community structure acting through a
filter to drive stability. However, the filter is different in each space; in
the first, the filter is the topology and the strength of species interactions
and in the second variation in species’ responses. Moreover, the theory has been
developed largely in theoretical or empirical communities characterised by a
limited array of interactions (e.g. often lacking in consumers) and by limited
species diversity/richness. Thus, ecology lacks a body of theory integrating
across structure and response diversity frameworks and reflecting species rich
communities. Here, we integrate these two perspectives on diversity - stability
to evaluate the combined effects of community structure and response diversity on
temporal stability in species rich, complex communities characterised by
competition and predation.

The ability to do this is supported by a key statistical advance: it is now
possible to partition asynchrony into two component sources, the statistical
averaging effect (SAE) and compensatory dynamics effect (CPE)
[@zhao_biodiversity_2022]. SAE quantifies the portfolio effect emerging from
independent species fluctuations, while CPE describes compensatory dynamics
emerging from species interactions and differential responses to environmental
stochasticity. This allows an unprecedented opportunity to obtain mechanistic
insight about the effects of stressors and food-web structure on stability in
complex, species rich communities.

Our primary objective is to derive theory that predicts how the components of
community stability, that can differentially drive patterns of stability, deliver novel
insights into the source and patterns of diversity-stability relationships in
complex communities facing environmental stochasticity. Our approach delivers
revised insight into diversity-productivity relationships in species rich
communities when both community structure per se, and species
responses can vary. In the following sections, we begin by introducing the
multi-species model and the features of the model that allow us to integrate
across variation in community structure and response diversity. We
then introduce assumptions we use to implement environmental stochasticity,
response diversity, variation in community structure and variation in the
distribution of interaction types and strengths. Next we define our in-silico
experimental design that specifically aligns with three core questions and
associated analyses: (1) What are the direct effects of food-web structure and
interaction strength on population stability, compensatory dynamics,
and statistical averaging effects (i.e. portefolio effects)? (2) What are the
total effects of food-web structure, reponse diversity, environmental
stochasticity on community stability. Finally merging the two parallel bodies of
work, we asked (3) How do response diversity and food-web structure interact to
drive the sign of the relation between community stability and
species richness?

---

#Here we deliver inference from modelling of complex biodiverse communities on
#how food-web structure (connectance, average interaction strength, average
#trophic level), response diversity, and environmental stochasticity combine to
#shape temporal stability of community biomass, as well as its partition into
#asynchrony and population stability. We then assess how food-web complexity and
#response diversity shape stability-richness relationships.

#Environmental forcing (such as food availability and
#warming) and land-use intensity was reported to synchronise population
#fluctuations [@benton_population_2001; @bluthgen_land_2016; @song_reduced_2015;
#@liu_aridity_2023] while habitat degradation tends to decrease population
#stability [@olivier_urbanization_2020]. Understanding the effects of global
#change on community temporal stability therefore require to account for their
#simultaneous effects on community and population scales [@kefi_advancing_2019;
#@simmons_refocusing_2021].

#Increasing species richness has been reported to decrease population stability
#in experimental grasslands [@tilman_biodiversity_2006;
#@roscher_identifying_2011], while increasing population stability in natural
#settings [@houlahan_negative_2018] [add mechanisms?]. In turn, higher species
#richness often results in higher asynchrony, through portfolio effects (i.e.
#statistical averaging effects due to independent species fluctuations) and
#compensatory dynamics (due to species interactions and response diversity of
#species due to the environment) [@loreau_species_2008;
#@thibaut_understanding_2013]. Systematic increase in asynchrony with species
#richness is the mechanism that drives reported positive relationships between
#community stability and species richness [ref]. Anthropogenic pressures, such as
#eutrophication, has been reported to weakens the relationship between species
#richness and asynchrony in grasslands [@hautier_eutrophication_2014] but such
#empirical evidence remains scarce. However, stressors such as biotic
#homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
#@saladin_rapid_2020] and environmental forcing that decrease species response
#diversity should dampens the relationships between asynchrony and species
#richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
#in portfolio effects and compensatory effects. [Talk about the effects of
#evenness in temporal variability and evenness in abundance? e.g.,
#@zhao_biodiversity_2022; @thibaut_understanding_2013]. Because stressors can
#affect both community stability per se and how community stability scales with
#species richness, improving our understanding require to study both
#[@ives_stability_2007; @hautier_anthropogenic_2015].

#including levels of generalism, the distribution of interaction strengths and
#the prevalence of omnivory, can also influence stability. The degree of
#generalism of predator was shown to modulate stability-richness relationships
#[@thebault_trophic_2005], and generalist predators can synchronise the dynamics
#of their preys[@raimondo_interspecific_2004]. The strength and distribution of
#interaction strength was also shown to be strong driver of community stability,
#such as stronger interaction strengths can be destabilizing [@may_will_1972;
#@mccann_weak_1998]. Omnivory was also shown to drive higher population stability
#[@mccann_reevaluating_1997]. The effects of food-web structure on ecosystem
#stability has been mostly assessed with small modules [but see
#@eschenbrenner_diversity_nodate], and we know very little how food-web structure
#affects the relationships between species richness and temporal stability in
#complex food-webs. So understanding the effects of stressors on community
#stability and on community stability-richness relationships necessitate to
#account for food-web structure.
---

@@

```{r}
met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
and high response diversity. b, simulations with low and high predator-prey mass
ratio (upper and bottom panels), low and high species richness (left and right
  panels). The food-web are displayed on the side with the node size
being proportional to the average species biomass across the simulation. We
also display the food-web structure and the stability metrics. Across all
simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1 and 100." %>%
  str_replace_all("\\s+", " ")
```

```{r met, fig.cap = met_cap}
knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
```

@@

We added a stochastic natural mortality rate to the species dynamics,
representing a fluctuating environment. Based on the literature and previous
models [@vasseur_environmental_2007], we assumed that
natural mortality rates scales inversely with the species body mass ($d_i =
d_0M_i^{-1/4}$), as all other physiological parameters. We used a basal
natural mortality rate of $d_0 = .4$, as done in previous
studies[@vasseur_environmental_2007].

@@

To vary interaction strength and mortality rates in the community,
we varied the Predator-Prey Bodysize Ratio (PPBR) from 1 to 100. We further
varied the functional response of consumer from type II to type III (resp. $h=2$
and $h=3$, eq XX) as it was shown to have a tremendous role on stability
[@brose_allometric_2006]. We set $K = 10$ to ensure that consumers were not
limited by the biomass input from primary producers.

@@

We numerically solved the simulations during 5000 timesteps
and collected the last 500 timesteps. We set $d_t = .1$, and $d_t = .05$ when
instability was detected during the simulations. We set extinction threshold to
$10^{-6}$ and if an extinction happened in the last 500 timesteps, we continued
to run the simulation for another 1000 timesteps until there was no extinction
events. When we found disconnected species at the end of the simulation (i.e. a
primary producer without consumer or a consumer without prey), we removed them
and re-run simulation for another 1000 timesteps.

@@

Regarding asynchrony, we tested the effects of species richness, connectance,
average trophic level and interaction strength on statistical averaging effects.
We expected that those same food-web structural properties affected
compensatory dynamics due to interactions ($CPE_{int}$). Finally, we tested the
effects of species richness and species response diversity in mortality rates on
the compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We
completed the structural equation model with the mathematical relationship
linking compensatory dynamics and statistical averaging effects to asynchrony,
and from asynchrony and population stability to community stability.

@@

In a second analysis, we aimed to test how stability-species richness
relationships were modulated by food-web structure and the two stressors:
environmental stochasticity and response diversity. We modelled temporal
stability of biomass according to food-web structure: species richness, weighted
average trophic level, connectance, hill exponent, predator-prey size ratio, and
average interaction strength, as well as environmental stochasticity and species
response diversity. We further included the two way interactions between species
richness and food-web structure, plus between species richness and stressors.
Finally we added the three way interaction between species richness, food-web
structure and stressors. The VIF were inferior to 5, indicating low
multicollinearity. We then used the coefficients of the model to predict the shape
of the relationship between community stability and species richness according
to a gradient of response diversity and of food-web structure.

@@

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  species response diversity. We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. A more complete SEM containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

@@

rcr <- get_eff(y = "cpe", x = "richness")
rci <- get_eff(y = "cpe", x = "avg_int_strength")
rcd <- get_eff(y = "cpe", x = "resp_div")

@@

rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
rvd <- get_eff(y = "cpe_env", x = "resp_div", tab = sem_eff_tab)
```
```{r, eval = FALSE}
sem_simplified_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```

@@

We further found that food-web structure had a strong impact on statistical
averaging effects, which raises from independent species fluctuations weighted
the evenness of their variance. As expected the mathematical relationship (eq.
XX), species richness was a main positive driver of statistical averaging effect
($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)), thereby increasing asynchrony.
Average trophic level and average interaction strength had strong negative
effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
`r rsi`), thereby downplaying the portfolio effect raised from species
richness. In turn, we found that average interaction strength had a small
positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
\@ref(fig:sem)). Species response diversity had a strong positive effect on compensatory dynamics
($r_\delta$= `r rcd`).

@@

```{r}
rtsdiv <- get_eff(y = "stab_com", x = "resp_div", effect_type = "total")
rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")

@@

Deriving the sum of direct and indirect effects from the structural equation
model, we show that both environmental stochasticity and response diversity among
species had by far the most important effect on community stability (resp.
$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:semtot)). Species richness
had a low overall positive total effect on community stability (`r rtsr`)
because its strong total positive effect on asynchrony (`r rtar`) was downplayed
by its total negative effect on population stability (`r rtpr`) and that the
weight of population stability on community stability is twice higher than the
one of asynchrony. Average trophic level, type III functional response and
predator prey bodysize ratio had positive effects on community stability in
total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:semtot)), driven by
their positive effects on population stability that were weakly counterbalanced
by their negative effects on asynchrony. In turn, connectance and average
interaction strength had low total negative effects on community stability (resp.
`r rtsc` and `r rtsi`, Fig. \@ref(fig:semtot)). While connectance had negative
effects both on population stability and asynchrony, average interaction
strength had a low total positive effect on population stability counterbalanced
by a stronger negative effect on asynchrony.

@@

```{r}
tar_load(default_variable_values_pred)
pv <- default_variable_values_pred
pv_cap <- paste0(
  "connectance = ", pv["ct_alive"],
  ", average interaction strength = ", pv["avg_int_strength"],
  ", average trophic level = ", pv["w_avg_tlvl"],
  ", hill exponent = ", pv["h"],
  ", Predator-Prey Mass Ration = ", pv["Z"],
  ", response diversity = ", pv["resp_div"],
  ", and environmental stochasticity = ", pv["env_stoch"]

@@

Using a more complex linear model (i.e. including interactions), we investigated
more in detail the relationship between community stability and species richness
and how this relation is affected by environmental stochasticity and species
response diversity. We found that environmental stochasticity decrease overall
community stability but has only little effect on the shape of the community
stability-species richness relationship (put some numbers, Fig. \@ref(fig:pred)a
and b). In contrasts, species response diversity both increases overall
community stability and leads to positive community stability-species richness
relationships. Surprisingly, we found that despite average interaction strength
has a small overall effect on community stability, high average interaction
strength change the shape of the community stability-species richness
relationship from positive to negative when response diversity is low (put some
numbers, Fig. \@ref(fig:pred)b).
